\subsection{Overview}
Find out a way to escape from a place you don’t know and where you’re locked in. Use your super powers and your mind to avoid guards, solve puzzles and discover all the secrets that cover the entire game.

\subsection{- Gameplay description}


\subsection{Controls}
\subsubsection{Interfaces}
\begin{itemize}  
\item Main menu: \begin{itemize}  
			\item "Start new game"
			\item "Load Game"
			\item "Select Level"
			\item "Settings"
			\end{itemize}
\item Settings:	\begin{itemize}  
			\item "Music volume"
			\item (Language)
			\item (Controls)
			\item (Video)
			\end{itemize}
\item Pause screen:	\begin{itemize}  
				\item "Resume"
				\item "Restart from last checkpoint"
				\item Mini map
				\item "Settings"
				\item "Quit"
				\end{itemize}
\item Game UI: \begin{itemize}  
			\item Change character
			\item Character movement
			\item Use power
			\item (Call mates (quick press: call nearby characters, long press: call all characters))
			\item Collect/Discard item
			\item Use item
			\item (Jump)
			\item Camera movement
			\item Pause
			\item Selected character indicator
			\end{itemize}
\end{itemize}

\subsubsection{Rules}
\begin{enumerate}  
\item If a guard reach you, you loose and restart from last checkpoint
\item If a guard see you, he/she starts to chase you
\item If an alarm rings all guards move into the room the sound come from
\item Characters power: 	\begin{itemize}
					\item Invisibility: invisible to all characters and environment elements (cameras). "Call mates" deactivated. Usable for a limited amount of time.
					\item Immateriality: invulnerable to fire, electricity and other things that can hurt you for a limited amount of time. Could pass through "blue" objects.
					\item Slow down time: for a limited amount of time you can slow down time. Only the character using the power maintain the same speed. 
					\end{itemize}
\end{enumerate}

\subsubsection{Scoring/winning conditions}
All characters reaches the end of the level

\subsection{- Levels}
\subsubsection{Introductory level}
This is an introductory level. Here are presented to the player the superpowers of the two protagonists.
This is the beginning of the history. Jake wakes up in an unknown place and near him he sees two other people (that will became his fellows). He doesn't remember how he is finished there.

\subsubsection{Intermediate level}
This is an intermediate level in which the three characters have to cooperate to exit between connected rooms.
The level is divided in two blocks (a checkpoint permit to the player to not restart from scratch the level in case of misses or errors).
In the first block there are some guardians that can block the characters if they enter in their seefield or in the seefield of the videocameras.
In the second block the characters are in a kind of a "safe" situation (no guardians can see them) and have to overcome some obstacles and traps to terminate the level.
Time to complete: 10/15 min

\subsubsection{Final level}
The final level consist in exit from a labirint whose map has to be given by the characters.
Time to complete: 5/10 min

\subsection{- Flowchart}
TO Do
