\subsection{Synopsis}
Dr. James Dertham is a scientist who's working on a new kind of energy reactor for European countries in a project called SONA (Super Optimized Neutrins Acceleration). During a test in a remote lab something goes wrong. The silent storm of death hits the nearby small village killing all of the inhabitants except three people and leaving behind a faint radiation.  The survivors are found by the army and they are confined in a secret lab to investigate how they survived the radiation.
They wake up in a dark room and they feel strange… 

\subsection{- Backstory}
Jack is Dr Dertham’s son and was employed in the lab with him. They had a dangerous experiment planned but deadline force them to take it before all required pre-tests were completed. So Dr. Dertham gave all the employees a licence day and did the experiment with his son. Jack was near the energy source and his father was operating on the console further away. Meanwhile Hannah and Charlie were robbing the local bank. While their gang were helding hostages on the ground level they were in the caveau picking the locks on the safe.
When the death storm is released Jack survived because he was in the eye of the storm, while Hannah and Charlie were protected in the caveau. 
The survivors are found by the army and they are confined in a secret lab on a ship to investigate how they survived the radiation.

\subsection{Complete story}
Jack wakes up in a mostly dark room with Charlie and Hannah staring at him. They tell him that they don't know why they are there, but they discovered to have superpowers once awake. Jack has lost his memory. Jack has no superpower at the beginning, but during the course of the game he starts to develop one.
In the final level the three guys reach the place where the findings on the lab site were stored. The objects include some taken from Dr. Dertham’s office. They find out the reason why they are there, the name of the marshall who put them there and all the story behind Dr. Dertham, his son and the SONA project.
While Jack and Hannah are investigating the last room, Charlie opens a double door (decontamination room) which leads to the bridge of a warship where marshall Derrick Stone is waiting for them. The game ends with the marshall welcoming them:_”Jack, without you this wouldn’t have happened. It’s better now to put those powers to use.”


\subsection{? Narrative devices}
\begin{itemize}  
\item Documents/newspaper
\begin{itemize}
\item photo with Jack and Dr. James Dertham
\item Economic Dossier about SONA project.
\item Dossier about the unusual activity before the experiment
\begin{itemize}  
\item Newspaper about a criminal gang (number of gang members+2)
\item Report about robbery (number of dead gang members, without Hannah and Charlie)
\end{itemize}
\item Jack’s, Hannah and Charlie subject folder (with radioactivity levels)
\item Documents in the SONA room
\begin{itemize}  
\item Dr. Dertham data about a dangerous experiment that should have been conducted two weeks later after more tests.
\item A Dr. Dertham’s note about a licence day for all employees 
\item Details of experiment to be conducted by two people, one near the energy source and the other further away.
\end{itemize}
\end{itemize}
\item Dialogs (?)
\end{itemize}

\subsection{- Subplots}
\begin{itemize}  
\item Charlie and Hannah survived the bomb because they were rubbing a bank caveau. 
\item Jack was the one who failed the experiment but he was in the eye of the storm so he got a superpower and lost his memory. His superpower is related on failure emotion: stronger is his emotion stronger will be his power. His father is Dr. Dertham
\item Dr Dertham died during the accident. 
\end{itemize} 
