\subsection{Overview}
The game is set on a platform surrounded by sea, which hosts the laboratory used for the studies 
on the main characters. The player will explore various rooms trying to get outside.
\subsection{Key locations}
\begin {itemize}
	\item Holding cell: the cell where the game starts. The characters were closed in there.
	\item Doctor's office: the characters will arrive there during their exploration. In the office they will find out the story behind their kidnapping
\end {itemize}
\subsection{Travel}
The characters will only move by foot.
%\subsection{- Mapping}
%\subsection{- Scale}
\subsection{Physical objects}
The objects in the game are divided into:
\begin {itemize}
	\item Obstacles: they include walls, doors and other unmovable objects that limit the movements of the player
	\item Movable objects: they are all kind of objects that can be moved. They can still partially limit, or otherwise modify, the movements of the player, but they can also be involved in the solution of the puzzles
	\item Items: objects that can be picked up and used. They don't affect the movements of the characters
	\item Characters: These objects have their own movement capabilities and can affect the game in different ways. If they don't trigger a reaction, they act as moving obstacles
\end {itemize}
%\subsection{- Weather conditions}
%As the game is set inside, the weather doesn't affect the gameplay
%\subsection{- Day and night}
%The game is set inside and there is no difference in gameplay between day and night.
\subsection{Time}
The story is told linearly from the beginning to the end and doesn't include flashbacks or 
anticipations. The flowing of time can be affected by powers in the game
%\subsection{- Physics}
%The game is set on the Earth surface and objects obey the common laws of physics, unless influenced by powers in the game
%\subsection{- Society/culture}
%The game is set in the current society